\documentclass[a4paper]{article}

% Import some useful packages
\usepackage[margin=0.5in]{geometry} % narrow margins
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage{minted}
\usepackage{amsmath}
\usepackage{xcolor}
\definecolor{LightGray}{gray}{0.95}

\title{Peer-review of assignment 4 for INF3331-juliaza}
\author{Reviewer 1, emilieeo, {emilieeo@math.uio.no} \\
 		Reviewer 2, magnukla, {magnukla@ifi.uio.no}}

\begin{document}
\maketitle


\section*{Review}
Mac OS Sierra 10.12 with python 3.5.2 was used to review this exercise. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{General feedback}
All code is very compact and well structured. Code is easy to read and the variables have sensible names. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 4.1: Python implementation}
The code runs as expected, and is well structured. Very well done!



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 4.2:  numpy implementation} \label{sec:assignment5.2}
The code runs as expected, and is very well commented and compact with vectorization and a clear speed-up. 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 4.3: Integrated C implementation}
The code runs as expected, again with a very clear speed-up. 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 4.4:  An alternative integrated C implementation}
Not applicable. 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 4.5: User interface}
The help message is well structured, and provides useful information on how to run the program. Easy to use command line interface, with a lot of options. All the required options are supported. 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 4.6:  Packaging and unit tests}
A well implemented program with two successful test runs. Good use of the UnitTest framework. 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 4.7: More color scales + art contest}
Well implemented program with all the required options as well as a color option. Very user friendly, and with a creative and beautiful contest image.  

\subsection*{Assignment 4.8: Self replication}
The code runs as expected, and it fulfills the assignment.


\bibliographystyle{plain}
\bibliography{literature}

\end{document}
